\documentclass[11pt,letterpaper]{article}

% Main document
\input{meta.tex}
\input{preamble.tex}

\begin{document}
\maketitle

\begin{abstract}

Many sensing devices rely on transduction mechanisms that convert mechanical deformation into measurable electrical signals.
A prominent example is the piezoresistive effect, where the electrical conductivity of a material varies under applied strain.

From a materials physics perspective, this behavior originates from strain-induced modifications of the electronic structure and carrier transport properties. 
Mechanical deformation alters band energies, effective masses, and scattering mechanisms, which in turn influence carrier mobility and electrical conductivity \cite{hamaguchi}. 
In certain regimes, additional effects such as tunneling may also contribute to the overall response.

This work develops a computational framework for modeling strain-dependent conductivity in deformable materials by connecting these physical mechanisms across scales.
At the continuum level, the mechanical behavior is described by the equations of elasticity, while the electrical response is governed by a conductivity equation with strain-dependent coefficients. 
This leads to a coupled system of partial differential equations of the form
\[
\nabla \cdot \boldsymbol{\sigma}(u) = 0, \qquad
\nabla \cdot \left( \sigma(\varepsilon(u)) \nabla V \right) = 0,
\]
where $u$ denotes the displacement field, $V$ the electrical potential, and $\sigma(\varepsilon(u))$ represents an effective conductivity incorporating the influence of mechanical deformation.

A central aspect of this study is the interpretation of the constitutive relation $\sigma(\varepsilon)$.
Rather than treating it purely phenomenologically, the framework is designed so that it can be informed by transport models derived from electronic structure calculations, providing a physically motivated link between microscopic behavior and macroscopic response.

From a computational perspective, the focus lies on the formulation and numerical solution of the coupled system using finite element methods.
A baseline case with constant conductivity is first analyzed and validated, followed by the extension to spatially varying, strain-dependent conductivity.
The framework is constructed to remain flexible, allowing the incorporation of physics-based models or data-driven approximations for $\sigma(\varepsilon)$.

The proposed approach provides a consistent and extensible pathway for studying electromechanical coupling in materials.
Potential applications include sensing technologies, flexible electronics, and structural health monitoring.

\end{abstract}

\tableofcontents

% Sections
\input{Sections/intro.tex}

\input{Sections/problem Articulation.tex}

\input{Sections/Problem Statement.tex}

\input{Sections/Mathematical Model.tex}

\input{Sections/ResearchState.tex}

\input{Sections/Method.tex}

\input{Sections/outcome.tex}


\clearpage
\printbibliography

\end{document}
