\section{Expected Outcome}

The expected outcome of this study is the development of a computational framework for analyzing strain-dependent electrical conduction 
in deformable materials. This framework will integrate continuum mechanics and electrical transport into a unified numerical model, 
allowing for the systematic investigation of electromechanical coupling.

At the modeling level, the work will provide a consistent formulation of conductivity as a strain-dependent quantity, 
together with a numerical implementation capable of solving the resulting coupled system. 
This will enable the exploration of how mechanical deformation influences electrical potential distribution, 
current density, and overall sensitivity of the system.

From a computational perspective, the study will deliver a flexible pipeline that can be adapted to different forms of the 
strain–conductivity relation, including both phenomenological models and more physically informed or data-driven descriptions. 
This makes the framework suitable for studying a range of materials and configurations.

Beyond the specific application, the results are expected to contribute to the broader understanding of nonlinear multiphysics systems, 
particularly those involving coupling between mechanical deformation and transport phenomena. 
Potential applications include piezoresistive sensing, structural health monitoring, and the design of flexible or functional materials.

The framework may also serve as a basis for future extensions toward multiscale or more detailed transport models.